---
title: "My Fancy Presentation"
author: "PG"
date: "3 Juni 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

### Two different kind of lists

A unordered list:

- Bullet 1
- Bullet 2
- Bullet 3

A ordered list:

1. Item a
2. Item b

***
A slide without a title

## Another slide

Plain text

*italicized text*

**Bold text**

Some code (not to be run):

`for (i %in% 1:10)`

## A slide with code to be run

```{r}
head(mtcars)
```

```{r, comment="", echo=TRUE}
head(mtcars)
```

## A slide with code to be run II

```{r, comment="", eval=FALSE}
# Doesn't show this comment unless global options are echo=TRUE
```

```{r, comment="", echo=TRUE, eval=FALSE}
head(mtcars)
```

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## My new slide

```{r, fig.align='center', fig.cap='My AWESOME figure'}
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab = "MPG")
```
